\LARGE \bf Attack Graph Generation for Micro-service Architecture

### 2018-04-30 paper_own_docker/main.tex
Updating .tex file with related work, and cleaning up the examples

>>>>

What makes us different to previous work:
- To the best of our knowledge, there is no work that has been done for attack graph generation for docker containers.
- The paper(Automated Generation of Attack Graphs Using NVD) does not provide an example/ or clearly define the attack graph generation process. Their main focus is to evaluate attack rules. They dont use Clair as well. They do not offer any performance comparison between different topologies.
